%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Bloomberg LP} % Organization
    {New York City} % Location
    {Apr. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a fullstack engineer on various internal tools for Bloomberg's security department}
      \end{cvitems}
    }

  \cventry
    {Fullstack Platform Engineer} % Job title
    {Lifion by ADP} % Organization
    {New York City} % Location
    {Feb. 2019 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built i18n pipeline for flagship end-user facing apps}
        \item {Built a service to streamline ETL pipeline transformation}
      \end{cvitems}
    }

  \cventry
    {Front End Engineer} % Job title
    {ITN Networks} % Organization
    {New York City} % Location
    {Jul. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on various features on the company's front end codebase with over 1.5 million lines of code with 10 other engineers using React}
        \item {Integrated Cypress testing automation and developed a more reliable end to end testing infrastructure} 
        \item {Aggressively refactored the codebase to improve performance, readability and maintainability} 
      \end{cvitems}
    }

  \cventry
    {Fullstack Software Engineer Consultant} % Job title
    {IrisVR Inc.} % Organization
    {New York City} % Location
    {Oct. 2016 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented build system on company's front end and desktop app development environment using Webpack}
        \item {Developed the company's front end client using React and Redux}
        \item {Developed the company's desktop client using Electron and React}
        \item {Designed failure-point handling to handle disconnections between several NodeJS backend services gracefully}
        \item {Migrated company's MongoDB and AWS Redshift database changes with ensured consistency}
      \end{cvitems}
    }

  \cventry
    {Co-founder \& Fullstack Software Engineer} % Job title
    {Ninthbeat Inc.} % Organization
    {New York City} % Location
    {Mar. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a marketplace platform for musicians to buy and sell their used musical instruments}
        \item {Utilized MEAN stack to develop a full-stack solution for the platform}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
